About

### 2019-05-27 analysis/about.Rmd
wflow_publish("analysis/about.Rmd")

- `analysis/01-download.R`
- `analysis/02-hyperspectral-processing.R`
- `analysis/04-data-processing.R`
- `analysis/05-modeling/`

@@

In addition, it contains the workflow for a sub-project: Predicting defoliation to the Basque Country (for the years 2017 and 2018) using Sentinel-2 data.

The following "targets" are important for this sub-project:

- `defoliation_raster` (in `analysis/03-sentinel-processing`)

@@

See the [`analysis`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis) directory on GitHub for the source code that generated the figures and statistical results contained in the manuscript.
See the [`data`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis/data) directory for instructions how to access the raw data discussed in the manuscript.

@@

# Licenses

Text: CC-BY-4.0 http://creativecommons.org/licenses/by/4.0/

Code: MIT http://opensource.org/licenses/MIT year: 2019, copyright holder: Patrick Schratz

Data: CC0 http://creativecommons.org/publicdomain/zero/1.0/

>>>>

- `code/01-download.R`
- `code/02-hyperspectral-processing.R`
- `code/04-data-processing.R`
- `code/05-modeling/`
- `code/06-benchmark-matrix/`
- `code/07-reports/`

@@

In addition, this repo contains the workflow for an analysis related to the [LIFE 14 ENV/ES/000179 LIFE HEALTHY FOREST](http://www.lifehealthyforest.com/) project: Predicting defoliation at trees for the Basque Country (for the years 2017 and 2018) using Sentinel-2 data.

Target `defoliation_maps_wfr` builds are targets necessary for the final results [report](https://2019-feature-selection.pjs-web.de/report-defoliation.html).

@@

See the [`code`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis) directory on GitHub for the source code that generated the figures and statistical results contained in the manuscript.
See the [`data`](https://github.com/pat-s/paper_hyperspectral/tree/master/analysis/data) directory for instructions how to access the raw data discussed in the manuscript.

@@
